\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-02-11 investigation/docs/overview.tex
edits to overview doc

\paragraph{Filter 2} We also performed a second filtering screen applied to the list of SNP pairs from stage 1 that was identical to filter 1 but an additional step was included where any SNPs that had previously been shown to have a significant additive or dominant effect ($p < 1.29 \times 10^{-11}$) were removed \cite{Powell2013}, creating a second set of 4751 unique filtered SNP pairs.

>>>>

\paragraph{Filter 2} We also performed a second filtering screen applied to the list of SNP pairs from stage 1 that was identical to filter 1 but an additional step was included where any SNPs that had previously been shown to have a significant additive or dominant effect ($p < 1.29 \times 10^{-11}$) were removed, creating a second set of 4751 unique filtered SNP pairs.
